---
title: "Main File for S2 main CAM study"
author: "Julius Fenn, Louisa Estadieu"
format:
  html:
    toc: true
    toc-depth: 3
    html-math-method: katex
---

```{r}
#| echo: false
#| warning: false
#| results: hide

# sets the directory of location of this script as the current directory
# setwd(dirname(rstudioapi::getSourceEditorContext()$path))

########################################
# load packages
########################################
require(pacman)
p_load('tidyverse', 'jsonlite', 'magrittr', 'xlsx',
       'stargazer', 'psych', 'jtools', 'DT', 'ggstatsplot', 
       'lavaan', 
       'regsem', 'MplusAutomation', 'igraph')

########################################
# list data files
########################################
setwd("data")
folders <- list.files(pattern = "^study_result.*")

########################################
# create data files - GERMANY
########################################
### get CAM data
writeLines("", "CAMdata.txt") # create file
text_connection <- file("CAMdata.txt", "a") # open connection to append

### get CAM data second
writeLines("", "secondCAMdata.txt") # create file
text_connection_second <- file("secondCAMdata.txt", "a") # open connection to append

### get pre CAM data
writeLines("", "preCAM.txt") # create file
text_connection_pre <- file("preCAM.txt", "a") # open connection to append

### get post CAM data
writeLines("", "postCAM.txt") # create file
text_connection_post <- file("postCAM.txt", "a") # open connection to append

### get post second CAM data
writeLines("", "secondPostCAM.txt") # create file
text_connection_postSecond <- file("secondPostCAM.txt", "a") # open connection to append

for(i in 1:length(folders)){
  setwd(folders[i])
  if(length(dir()) == 5){
    # print(i)
    ### CAM data
    setwd(dir()[2])
    tmp <- jsonlite::fromJSON(txt = "data.txt")
    writeLines(jsonlite::toJSON(x = tmp), text_connection)
    setwd("..")

    ### pre CAM data
    setwd(dir()[1])
    tmp <- jsonlite::fromJSON(txt = "data.txt")
    writeLines(jsonlite::toJSON(x = tmp), text_connection_pre)
    setwd("..")

    ### post CAM data
    setwd(dir()[3])
    tmp <- jsonlite::fromJSON(txt = "data.txt")
    writeLines(jsonlite::toJSON(x = tmp), text_connection_post)
    setwd("..")
    
    ### CAM data second
    setwd(dir()[4])
    tmp <- jsonlite::fromJSON(txt = "data.txt")
    writeLines(jsonlite::toJSON(x = tmp), text_connection_second)
    setwd("..")
    
    ### post CAM data second
    setwd(dir()[5])
    tmp <- jsonlite::fromJSON(txt = "data.txt")
    writeLines(jsonlite::toJSON(x = tmp), text_connection_postSecond)
    setwd("..")
  }
  setwd("..")
}

close(text_connection) # close connection CAM
close(text_connection_pre) # close connection
close(text_connection_post) # close connection
close(text_connection_second) # close connection CAM
close(text_connection_postSecond) # close connection

########################################
# move files to output folder
########################################
### copy files (not overwritten)
tmp_file_from <-  getwd()
setwd("../outputs")
file.copy(from =  paste0(tmp_file_from, "/CAMdata.txt"), to = paste0(getwd(), "/CAMdata.txt"))
file.copy(from =  paste0(tmp_file_from, "/preCAM.txt"), to = paste0(getwd(), "/preCAM.txt"))
file.copy(from =  paste0(tmp_file_from, "/postCAM.txt"), to = paste0(getwd(), "/postCAM.txt"))
file.copy(from =  paste0(tmp_file_from, "/secondPostCAM.txt"), to = paste0(getwd(), "/secondPostCAM.txt"))
file.copy(from =  paste0(tmp_file_from, "/secondCAMdata.txt"), to = paste0(getwd(), "/secondCAMdata.txt"))

### remove files
file.remove(paste0(tmp_file_from, "/CAMdata.txt"))
file.remove(paste0(tmp_file_from, "/preCAM.txt"))
file.remove(paste0(tmp_file_from, "/postCAM.txt"))
file.remove(paste0(tmp_file_from, "/secondPostCAM.txt"))
file.remove(paste0(tmp_file_from, "/secondCAMdata.txt"))

########################################
# load functions
########################################
print(getwd())
setwd("../../../functions")
for(i in 1:length(dir())){
  # print(dir()[i])
  source(dir()[i], encoding = "utf-8")
}


setwd("../functions_CAMapp")
for(i in 1:length(dir())){
  # print(dir()[i])
  source(dir()[i], encoding = "utf-8")
}
rm(i)



# summary function
data_summary <- function(data, varname, groupnames){
  require(plyr)
  summary_func <- function(x, col){
    c(mean = mean(x[[col]], na.rm=TRUE),
      se = sd(x[[col]], na.rm=TRUE) / sqrt(length(x[[col]])))
  }
  data_sum<-ddply(data, groupnames, .fun=summary_func,
                  varname)
  data_sum <- plyr::rename(data_sum, c("mean" = varname))
  return(data_sum)
}
```

# Notes


# prepare data

## set up data.frame questionnaires


```{r}
setwd("outputs")
# > pre study
suppressMessages(read_file('preCAM.txt') %>%
                   # ... split it into lines ...
                   str_split('\n') %>% first() %>%
                   # ... filter empty rows ...
                   discard(function(x) x == '') %>%
                   discard(function(x) x == '\r') %>%
                   # ... parse JSON into a data.frame
                   map_dfr(fromJSON, flatten=TRUE)) -> dat_preCAM
# > post first CAM
suppressMessages(read_file('postCAM.txt') %>%
                   # ... split it into lines ...
                   str_split('\n') %>% first() %>%
                   # ... filter empty rows ...
                   discard(function(x) x == '') %>%
                   discard(function(x) x == '\r') %>%
                   # ... parse JSON into a data.frame
                   map_dfr(fromJSON, flatten=TRUE)) -> dat_postCAM

# > post second CAM
suppressMessages(read_file('secondPostCAM.txt') %>%
                   # ... split it into lines ...
                   str_split('\n') %>% first() %>%
                   # ... filter empty rows ...
                   discard(function(x) x == '') %>%
                   discard(function(x) x == '\r') %>%
                   # ... parse JSON into a data.frame
                   map_dfr(fromJSON, flatten=TRUE)) -> dat_secondPostCAM



########################################
# create counter variable for both data sets
########################################
### pre study
dat_preCAM$ID <- NA

tmp_IDcounter <- 0
for(i in 1:nrow(dat_preCAM)){
  if(!is.na(dat_preCAM$sender[i]) && dat_preCAM$sender[i] == "Greetings"){
    # tmp <- dat_preCAM$prolific_pid[i]
    tmp_IDcounter = tmp_IDcounter + 1
  }
  dat_preCAM$ID[i] <- tmp_IDcounter
}



### post study
dat_postCAM$ID <- NA

tmp_IDcounter <- 0
for(i in 1:nrow(dat_postCAM)){
  if(!is.na(dat_postCAM$sender[i]) && dat_postCAM$sender[i] == "CAMfeedbackGeneral"){
    # tmp <- dat_postCAM$prolific_pid[i]
    tmp_IDcounter = tmp_IDcounter + 1
  }
  dat_postCAM$ID[i] <- tmp_IDcounter
}

### second post study
#> fix error in "sender variable"
for(i in 1:nrow(dat_secondPostCAM)){
  if(is.na(dat_secondPostCAM$sender[i])){
    if(!is.na(dat_secondPostCAM$sender[i+1])){
      dat_secondPostCAM$sender[i] <- "adaptiveAnswer"
    }
  }
}



dat_secondPostCAM$ID <- NA
tmp_IDcounter <- 0
for(i in 1:nrow(dat_secondPostCAM)){
  if(!is.na(dat_secondPostCAM$sender[i]) && dat_secondPostCAM$sender[i] == "adaptiveAnswer"){
    # tmp <- dat_secondPostCAM$prolific_pid[i]
    tmp_IDcounter = tmp_IDcounter + 1
  }
  dat_secondPostCAM$ID[i] <- tmp_IDcounter
}


########################################
# keep only complete data sets
########################################
### pre-study
# sort(table(dat_preCAM$ID))
sum(table(dat_preCAM$ID) != max(table(dat_preCAM$ID)))
sum(table(dat_preCAM$ID) == max(table(dat_preCAM$ID)))

dat_preCAM <- dat_preCAM[dat_preCAM$ID %in% names(table(dat_preCAM$ID))[table(dat_preCAM$ID) == max(table(dat_preCAM$ID))],]

### post-study
# sort(table(dat_postCAM$ID))
sum(table(dat_postCAM$ID) != max(table(dat_postCAM$ID)))
sum(table(dat_postCAM$ID) == max(table(dat_postCAM$ID)))

# dat_postCAM <- dat_postCAM[dat_postCAM$ID %in% names(table(dat_postCAM$ID))[table(dat_postCAM$ID) == max(table(dat_postCAM$ID))],]
dat_postCAM <- dat_postCAM[dat_postCAM$ID %in% names(table(dat_postCAM$ID))[table(dat_postCAM$ID) >= 4],]

### post-study second
# sort(table(dat_secondPostCAM$ID))
sum(table(dat_secondPostCAM$ID) != max(table(dat_secondPostCAM$ID)))
sum(table(dat_secondPostCAM$ID) == max(table(dat_secondPostCAM$ID)))

# dat_secondPostCAM <- dat_secondPostCAM[dat_secondPostCAM$ID %in% names(table(dat_secondPostCAM$ID))[table(dat_secondPostCAM$ID) == max(table(dat_secondPostCAM$ID))],]
dat_secondPostCAM <- dat_secondPostCAM[dat_secondPostCAM$ID %in% names(table(dat_secondPostCAM$ID))[table(dat_secondPostCAM$ID) >= 11],]



########################################
# json (from JATOS) to 2D data.frame
########################################
################################ pre-study
### !!! add paradata
vec_ques <- c("PROLIFIC_PID",
                "choosen_Robot", 
              "dummy_informedconsent", 
              "commCheck")

vec_notNumeric = c("PROLIFIC_PID",
                "choosen_Robot")

questionnaire_preCAM <- questionnairetype(dataset = dat_preCAM, 
                                        listvars = vec_ques, 
                                        notNumeric = vec_notNumeric, verbose = FALSE)


dim(questionnaire_preCAM)



################################ post-study

################################ post-study second
tmp_numeric <- str_subset(string = colnames(dat_secondPostCAM), pattern = "^GAToRS|^Almere|^LiWang")


vec_ques <- c("ans1",
                tmp_numeric,
                "feedback_critic")

vec_notNumeric = c("ans1",
                   "feedback_critic")

questionnaire_secondPostCAM <- questionnairetype(dataset = dat_secondPostCAM, 
                                        listvars = vec_ques, 
                                        notNumeric = vec_notNumeric, verbose = FALSE)


dim(questionnaire_secondPostCAM)
```



## set up CAM data

### pre

Load CAM data

```{r, message = FALSE}
setwd("outputs")
suppressMessages(read_file("CAMdata.txt") %>%
  # ... split it into lines ...
  str_split('\n') %>% first() %>%
    discard(function(x) x == '') %>%
    discard(function(x) x == '\r') %>%
  # ... filter empty rows ...
  discard(function(x) x == '')) -> dat_CAM_pre

raw_CAM_pre <- list()
for(i in 1:length(dat_CAM_pre)){
  raw_CAM_pre[[i]] <- jsonlite::fromJSON(txt = dat_CAM_pre[[i]])
}
```

Create CAM files, draw CAMs and compute network indicators

```{r, message = FALSE}
########################################
# create CAM single files (nodes, connectors, merged)
########################################
CAMfiles_pre <- create_CAMfiles(datCAM = raw_CAM_pre, reDeleted = TRUE)

########################################
# draw CAMs
########################################
CAMdrawn_pre <- draw_CAM(dat_merged = CAMfiles_pre[[3]],
                     dat_nodes = CAMfiles_pre[[1]],ids_CAMs = "all",
                     plot_CAM = FALSE,
                     useCoordinates = TRUE,
                     relvertexsize = 3,
                     reledgesize = 1)

########################################
# draw CAMs
########################################
tmp_microIndicator <- c("Rettungsroboter", "sozialer Assistenzroboter", "Vorteile", "Nachteile")
networkIndicators_pre <- compute_indicatorsCAM(drawn_CAM = CAMdrawn_pre, 
                                           micro_degree = tmp_microIndicator, 
                                           micro_valence = tmp_microIndicator, 
                                           micro_centr_clo = tmp_microIndicator, 
                                           micro_transitivity = tmp_microIndicator, 
                                           largestClique = FALSE)


########################################
# wordlists
########################################
CAMwordlist_pre <- create_wordlist(
  dat_nodes =  CAMfiles_pre[[1]],
  dat_merged =  CAMfiles_pre[[3]],
  order = "frequency",
  splitByValence = FALSE,
  comments = TRUE,
  raterSubsetWords = NULL,
  rater = FALSE
)

DT::datatable(CAMwordlist_pre, options = list(pageLength = 5)) 
```


### save CAMs as .json files, and as .png (igraph)


```{r saveCAMs_pictures_pre, message = FALSE}
save_CAMs_as_pictures = FALSE

if(save_CAMs_as_pictures){
  setwd("outputs")

setwd("savedCAMs_pre")
setwd("png")
### remove all files if there are any
if(length(list.files()) >= 1){
  file.remove(list.files())
  cat('\n!
      all former .png files have been deleted')
}

### if no participant ID was provided replace by randomly generated CAM ID

if(all(CAMfiles_pre[[3]]$participantCAM.x == "noID")){
  CAMfiles_pre[[3]]$participantCAM.x <- CAMfiles_pre[[3]]$CAM.x
}

### save as .json files, and as .png (igraph)
ids_CAMs <- unique(CAMfiles_pre[[3]]$participantCAM.x); length(ids_CAMs)


for(i in 1:length(ids_CAMs)){
  save_graphic(filename = paste0("CAM_", i, "_t1")) #  paste0(ids_CAMs[i]))
  CAM_igraph <- CAMdrawn_pre[[c(1:length(CAMdrawn_pre))[
    names(CAMdrawn_pre) == paste0(unique(CAMfiles_pre[[3]]$participantCAM.x)[i])]]]
  plot(CAM_igraph, edge.arrow.size = .7,
       layout=layout_nicely, vertex.frame.color="black", asp = .5, margin = -0.1,
       vertex.size = 10, vertex.label.cex = .9)
  dev.off()
}

setwd("../json")
### remove all files if there are any
if(length(list.files()) >= 1){
  file.remove(list.files())
  cat('\n!
      all former .json files have been deleted')
}
for(i in 1:length(raw_CAM_pre)){
  if(!is_empty(raw_CAM_pre[[i]]$nodes)){
    if(nrow(raw_CAM_pre[[i]]$nodes) > 5){
      write(toJSON(raw_CAM_pre[[i]], encoding = "UTF-8"),
            paste0(raw_CAM_pre[[i]]$idCAM, ".json"))
    }
  }
}
}
```

### post

Load CAM data

```{r, message = FALSE}
setwd("outputs")
suppressMessages(read_file("secondCAMdata.txt") %>%
  # ... split it into lines ...
  str_split('\n') %>% first() %>%
    discard(function(x) x == '') %>%
    discard(function(x) x == '\r') %>%
  # ... filter empty rows ...
  discard(function(x) x == '')) -> dat_CAM_post

raw_CAM_post <- list()
for(i in 1:length(dat_CAM_post)){
  raw_CAM_post[[i]] <- jsonlite::fromJSON(txt = dat_CAM_post[[i]])
}
```

Create CAM files, draw CAMs and compute network indicators

```{r, message = FALSE}
########################################
# create CAM single files (nodes, connectors, merged)
########################################
CAMfiles_post <- create_CAMfiles(datCAM = raw_CAM_post, reDeleted = TRUE)

########################################
# draw CAMs
########################################
CAMdrawn_post <- draw_CAM(dat_merged = CAMfiles_post[[3]],
                     dat_nodes = CAMfiles_post[[1]],ids_CAMs = "all",
                     plot_CAM = FALSE,
                     useCoordinates = TRUE,
                     relvertexsize = 3,
                     reledgesize = 1)

########################################
# draw CAMs
########################################
tmp_microIndicator <- c("Rettungsroboter", "sozialer Assistenzroboter", "Vorteile", "Nachteile")
networkIndicators_post <- compute_indicatorsCAM(drawn_CAM = CAMdrawn_post, 
                                           micro_degree = tmp_microIndicator, 
                                           micro_valence = tmp_microIndicator, 
                                           micro_centr_clo = tmp_microIndicator, 
                                           micro_transitivity = tmp_microIndicator, 
                                           largestClique = FALSE)


########################################
# wordlists
########################################
CAMwordlist_post <- create_wordlist(
  dat_nodes =  CAMfiles_post[[1]],
  dat_merged =  CAMfiles_post[[3]],
  order = "frequency",
  splitByValence = FALSE,
  comments = TRUE,
  raterSubsetWords = NULL,
  rater = FALSE
)

DT::datatable(CAMwordlist_post, options = list(pageLength = 5)) 
```


### save CAMs as .json files, and as .png (igraph)


```{r saveCAMs_pictures_post, message = FALSE}
save_CAMs_as_pictures = FALSE

if(save_CAMs_as_pictures){
  setwd("outputs")

setwd("savedCAMs_post")
setwd("png")
### remove all files if there are any
if(length(list.files()) >= 1){
  file.remove(list.files())
  cat('\n!
      all former .png files have been deleted')
}

### if no participant ID was provided replace by randomly generated CAM ID

if(all(CAMfiles_post[[3]]$participantCAM.x == "noID")){
  CAMfiles_post[[3]]$participantCAM.x <- CAMfiles_post[[3]]$CAM.x
}

### save as .json files, and as .png (igraph)
ids_CAMs <- unique(CAMfiles_post[[3]]$participantCAM.x); length(ids_CAMs)


for(i in 1:length(ids_CAMs)){
  save_graphic(filename = paste0("CAM_", i, "_t2")) #  paste0(ids_CAMs[i], "_t2"))
  CAM_igraph <- CAMdrawn_post[[c(1:length(CAMdrawn_post))[
    names(CAMdrawn_post) == paste0(unique(CAMfiles_post[[3]]$participantCAM.x)[i])]]]
  plot(CAM_igraph, edge.arrow.size = .7,
       layout=layout_nicely, vertex.frame.color="black", asp = .5, margin = -0.1,
       vertex.size = 10, vertex.label.cex = .9)
  dev.off()
}

setwd("../json")
### remove all files if there are any
if(length(list.files()) >= 1){
  file.remove(list.files())
  cat('\n!
      all former .json files have been deleted')
}
for(i in 1:length(raw_CAM_post)){
  if(!is_empty(raw_CAM_post[[i]]$nodes)){
    if(nrow(raw_CAM_post[[i]]$nodes) > 5){
      write(toJSON(raw_CAM_post[[i]], encoding = "UTF-8"),
            paste0(raw_CAM_post[[i]]$idCAM, ".json"))
    }
  }
}
}
```


# analyze data 



## group comparisons


```{r}
networkIndicators_pre$timepoint <- "pre"
networkIndicators_post$timepoint <- "post"



networkIndicators <- rbind(networkIndicators_pre, networkIndicators_post)

### add type robot
networkIndicators$typeRobot <- ifelse(test = !is.na(networkIndicators$valence_micro_Rettungsroboter), yes = "rescue robots", no = "socially assistive robots")
table(networkIndicators$typeRobot)

### add ID
networkIndicators$ID <- c(1:(nrow(networkIndicators) / 2), 1:(nrow(networkIndicators) / 2))

########################################
# show which robot was on average perceived more positive (overall data set)
########################################
summary(networkIndicators$mean_valence_macro[!is.na(networkIndicators$valence_micro_Rettungsroboter)])
summary(networkIndicators$mean_valence_macro[!is.na(networkIndicators$valence_micro_sozialerAssistenzroboter)])

########################################
# post - pre difference of robot -> average valence
########################################

############
# overall
############
### overall
hist(networkIndicators_post$mean_valence_macro - networkIndicators_pre$mean_valence_macro)
summary(networkIndicators_post$mean_valence_macro - networkIndicators_pre$mean_valence_macro)

ggwithinstats(
  data = networkIndicators,
  x = timepoint,
  y = mean_valence_macro
)


# table(networkIndicators$ID, networkIndicators$typeRobot)

############
# separated by robots - mean valence
############
# fit1 <- afex::aov_car(mean_valence_macro ~ timepoint*typeRobot + Error(ID / timepoint),
#                       data = networkIndicators)
# plot(CAMdrawn_pre[[53]])
# plot(CAMdrawn_post[[53]])
# plot(CAMdrawn_pre[[70]])
# plot(CAMdrawn_post[[70]])
networkIndicators_anova <- networkIndicators[!networkIndicators$ID %in% c(53, 70),]

fit1 <- afex::aov_car(mean_valence_macro ~ timepoint*typeRobot + Error(ID / timepoint),
                      data = networkIndicators_anova)
fit1a <- afex::aov_ez(id = "ID", dv = "mean_valence_macro",
                      data = networkIndicators_anova, between=c("typeRobot"), within=c("timepoint"))
# partical eta squared
anova(fit1, es = "pes")
# generalized eta squared
fit1a # > identical results


dfvalcor <- data_summary(networkIndicators_anova, varname="mean_valence_macro",
                         groupnames=c("timepoint","typeRobot"))
p <- ggplot(dfvalcor, aes(x=timepoint, y=mean_valence_macro, fill=typeRobot)) +
  geom_bar(stat="identity", color="black",
           position=position_dodge()) +
  geom_errorbar(aes(ymin=mean_valence_macro-se, ymax=mean_valence_macro+se), width=.2,
                position=position_dodge(.9)) + ggplot_theme + ylab(label = "average emotional evaluation")
print(p)

############
# separated by robots - number of concepts
############
fit1 <- afex::aov_car(num_nodes_macro ~ timepoint*typeRobot + Error(ID / timepoint),
                      data = networkIndicators_anova)
fit1a <- afex::aov_ez(id = "ID", dv = "num_nodes_macro",
                      data = networkIndicators_anova, between=c("typeRobot"), within=c("timepoint"))
# partical eta squared
anova(fit1, es = "pes")
# generalized eta squared
fit1a # > identical results


dfvalcor <- data_summary(networkIndicators_anova, varname="num_nodes_macro",
                         groupnames=c("timepoint","typeRobot"))
p <- ggplot(dfvalcor, aes(x=timepoint, y=num_nodes_macro, fill=typeRobot)) +
  geom_bar(stat="identity", color="black",
           position=position_dodge()) +
  geom_errorbar(aes(ymin=num_nodes_macro-se, ymax=num_nodes_macro+se), width=.2,
                position=position_dodge(.9)) + ggplot_theme + ylab(label = "number of drawn concepts")
print(p)




########################################
# post - pre difference of robot -> average number of concepts
########################################
ggwithinstats(
  data = networkIndicators,
  x = timepoint,
  y = num_nodes_macro
)
```
## open text answers

```{r}

questionnaire_secondPostCAM$meanDifferencesCAMs <- round(x = networkIndicators_post$mean_valence_macro - networkIndicators_pre$mean_valence_macro, digits = 2)
DT::datatable(questionnaire_secondPostCAM[,c("meanDifferencesCAMs", "ans1", "feedback_critic")], options = list(pageLength = 5)) 
```


# check questions

```{r}
###
c("63b87d2c9edd47ad702413a1", "5edc8e2eaa0f2295a0fcef85", "6529483ef2abe408d574860a") %in% questionnaire_preCAM$PROLIFIC_PID
###

tmpID <- questionnaire_preCAM$ID[questionnaire_preCAM$PROLIFIC_PID == "63b87d2c9edd47ad702413a1"]
plot(CAMdrawn_pre[[tmpID]])
plot(CAMdrawn_post[[tmpID]])

tmpID <- questionnaire_preCAM$ID[questionnaire_preCAM$PROLIFIC_PID == "5edc8e2eaa0f2295a0fcef85"]
plot(CAMdrawn_pre[[tmpID]])
plot(CAMdrawn_post[[tmpID]])

tmpID <- questionnaire_preCAM$ID[questionnaire_preCAM$PROLIFIC_PID == "6529483ef2abe408d574860a"]
plot(CAMdrawn_pre[[tmpID]])
plot(CAMdrawn_post[[tmpID]])
```

